### 2022-02-10 chapter5/chapter.tex
.

\begin{thm}
	For all \(\bs y_0^{(p)}=(\ell,\bs a_{\ell_0,i}^{(p)}(x_0),i)\), \(\ell_0\in\mathcal K\), \(x_0\in\mathcal D_{\ell_0,i}\), \(i\in\calS\), and any bounded function \(\psi:\mathbb R\times \mathcal S \to \mathbb R\), then
	\begin{align}
			&\mathbb E\left[\psi( \mathcal R(L^{(p)}(t),\bs A^{(p)}(t),\varphi(t)),\varphi(t) )   \mid \bs Y^{(p)}(0)=\bs y_0^{(p)} \right] \nonumber 
			\to \mathbb E\left[\psi({\bs X}(t))\mid \bs X(0)=(x_0, i) \right] \nonumber
	\end{align}
	weakly in \(t\) as \(p\to \infty\). 
\end{thm}
\begin{proof}
	Combine the Extended Continuity Theorem for Laplace transforms \cite[Chapter XIII, Theorem 2a]{feller1957} with the convergence of Laplace transforms in Corollary~\ref{cor: lk}. 
\end{proof}

>>>>

\begin{thm}\label{thm: big thm}
	For all \(\bs y_0^{(p)}=(\ell,\bs a_{\ell_0,i}^{(p)}(x_0),i)\), \(\ell_0\in\mathcal K\), \(x_0\in\mathcal D_{\ell_0,i}\), \(i\in\calS\), and any bounded function \(\psi:\mathbb R\times \mathcal S \to \mathbb R\), then
	\begin{align}
			&\mathbb E\left[\psi( \mathcal R(L^{(p)}(t),\bs A^{(p)}(t),\varphi(t)),\varphi(t) )   \mid \bs Y^{(p)}(0)=\bs y_0^{(p)} \right] \nonumber 
			\to \mathbb E\left[\psi({\bs X}(t))\mid \bs X(0)=(x_0, i) \right] \nonumber
	\end{align}
	weakly in \(t\) as \(p\to \infty\). 
\end{thm}
\begin{proof}
	Combine the Extended Continuity Theorem for Laplace transforms \cite[Chapter XIII, Theorem 2a]{feller1957} with the convergence of Laplace transforms in Corollary~\ref{cor: lk}. 
\end{proof}
